\documentclass{article}
\usepackage{hyperref}
 \usepackage{graphicx}
\usepackage[utf8]{inputenc}

\title{Module 4: Literature Review and Software Tooling}
\author{vaddadi venkatesh }
\date{December 2020}

\begin{document}

\maketitle

\section{Question:1}
Create a bibliography file related to your research topic and review atleast 2 research papers listing major strengths and weakness of the presented work in the research papers.
\subsection{ Needs to create a .bib file and upload it.}
\subsection{Two key Research papers (citation in IEEE Style) – with DOI link}
I have added following two research papers:

\begin{enumerate}
  \item Quantitative susceptibility mapping using deep neural network:QSMnet \cite{qsm}
  
  \item MoDL \cite{modl} :Model Based Deep Learning Architecture for Inverse Problems
\end{enumerate}

\subsection{ List Major Strength and weakness of each paper
    Strength:}
    
    
\subsubsection{QSMnet:}


\textbf{Strengths:}
Constructs the high quality susceptibility mapping from single orientation data. Even though the data is single orientation data, the results are very close gold-standard COSMOS QSM maps.

\textbf{Weakness:}
QSMnet has very deep architecture. Therefore, it needs lot of computational power.Since, it is in the clinical applications it is very important to check the reliability.

\subsubsection{MoDL: Model Based Deep Learning Architecture
for Inverse Problems}

\textbf{Strengths:}
MoDL merges the power of Model based construction schemes and deep learning. Therefore, it shows the data consistency and denoisng both.

\textbf{Weakness:}
It doesn't provided theoretical analysis on the convergence. In this proposed approach the number of iterations are fixed.
\section{Question:2}
Create a github pages of your own.
\subsection{One your home page (could be google pages as well)}
The following is the link for my home page:

\href{https://sites.google.com/view/vaddadivenkatesh/home}{https://sites.google.com/view/vaddadivenkatesh/home}
\subsection{One your projects page}
The following is the link for my projects page:

\href{https://sites.google.com/view/vaddadivenkatesh/projects}{https://sites.google.com/view/vaddadivenkatesh/projects}
\bibliographystyle{IEEEtran}
\bibliography{biblography.bib}

\end{document}
